r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2021-01-25 r-package/paper2020/paper2020.Rmd
knit new version of paper2020

<!-- It might be worthwhile to consider changing the defaults to use a longer time window, and to return more percentiles, so users don't have to set parameters to see variation -MWC -->
Since service levels can significantly vary across the day [@stepniak2019impact], r5r provides a `time_window` parameter. When this parameter is set, R5 will compute travel times for trips at the specified departure time and every minute for `time_window` minutes after. The `percentiles` parameter allows the user to retrieve travel time estimates at different points of the distribution (by default the median). These percentiles reflect service variation over the time window, but do not reflect schedule deviation not represented in the GTFS, though tools exist to create GTFS which reflects schedule deviations [@wessel2017constructing].

@@

<!-- For this map and the next, I couldn't figure it out but there must be a way to crop the map view so only the shaded
     portion is visible? -MWC -->

>>>>

Since service levels can significantly vary across the day [@stepniak2019impact], r5r provides a `time_window` parameter. When this parameter is set, R5 will compute travel times for trips at the specified departure time and every minute for `time_window` minutes after. The `percentiles` parameter allows the user to retrieve travel time estimates at different points of the distribution (by default the median). These percentiles reflect service variation over the time window, but do not reflect schedule deviation not represented in the GTFS, though tools exist to create GTFS which reflects schedule deviations [@wessel2017constructing].

@@
